### 2021-02-01 input/abstract.tex
coloring figures, adding biblio, sketching abstract

\TODO{Locating the closest copy of a specific content across a
  distributed infrastructure requires to keep up-to-date an index of
  all replicas and their respective locations. Existing methods mostly
  rely on an external service to store this index, either on a
  centralized server or using a Distributed Hash Table (DHT). However,
  contacting a remote node to obtain localization information
  contradicts with emerging Fog infrastructures in terms of locality
  and robustness. In this paper, we present $A^3$, an epidemic
  protocol that will efficiently inform the relevant nodes about the
  presence of replicas in their neighborhood. Upon the exchange of
  messages, each node maintains a personalized index that will
  eventually contain the location of the closest copy for each object
  according to its place in the network topology. We implemented $A^3$
  and deployed it on a dedicated testbed with real-world
  topologies. Experimental results show that the time to retrieve
  objects is significantly decreased from 10\% up to 60\%, when
  compared to a DHT-based localization service.}

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

>>>>

  Fog infrastructures allows content providers to better distribute
  data over autonomous systems, hence improving on quality of user
  experience by reducing latency. However, locating the closest data
  sources can prove challenging in dynamic networks with dynamic
  sources. Locating sources may effectively take more time than
  actually downloading contents. \TODO{Related work ?} In this paper,
  we introduce \NAME, a reactive protocol for dynamic logical
  partitioning in dynamic networks. \TODO{source automatically create
    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
    flooding}). \TODO{costs of operations.} When the system becomes
  quiescent, every process eventually converges to its closest
  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
    testbed?}

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-02-01 input/background.tex
coloring figures, adding biblio, sketching abstract

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with contained
      broadcast.}
  \end{center}
\end{figure*}

@@

Algorithm~\ref{algo:add} shows the instructions that implement the
rules of Definition~\ref{def:transitivedelivery} to converge towards
optimal partitioning. Figure~\ref{fig:add} illustrates its behavior on
a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition. They initialize their own
state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition. At scale, it saves bandwidth by limiting generated traffic
to subsets of processes. In Figure~\ref{fig:addD}, processes discard
last transiting messages. The system converged to the optimal
partitioning.  Transitive relationships ensure that each process gets
its closest source while accumulation of weights ensures that messages
propagation terminates.  Interestingly, while the receipt order of
messages does not impact on local control information
($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1}) \Leftrightarrow
r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
\TODO{d_b(\alpha_a^{1})}$), it impacts on control information
broadcast in the network ($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1})
\implies b_b(\alpha_{b}^{1.5}) \cdot b_b(\alpha_{b}^{1})$ while
$r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
b_b(\alpha_a^{1})$).

@@

One could solve this issue by using a conflict-free replicated data
type for set data structures, then deliver and broadcast all
operations to all processes~\REF. However, this would be costly in
terms of generated traffic with some processes delivering and
broadcasting unrelated to their partitions \TODO{(include locality)}.
One could also solve this issue by removing partitions that were not
advertised for a defined time~\REF. However, relying on physical
timeout could lead to either premature removals of partitions when
they are still operating; or slow convergence where processes believe
they belong to a partition that was removed.

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{fig:del}Partition removals cannot rely only on
    current partition, for it may lead to inconsistent partitioning.}
\end{figure*}

\begin{problem}[Consistent partitioning]
  \TODO{How to enable \emph{consistent} dynamic optimal partitioning
    in dynamic network with contained broadcast?}
\end{problem}

>>>>

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with scoped flooding.}
  \end{center}
\end{figure*}

@@

Algorithm~\ref{algo:add} shows the instructions that implement the
rules of Definition~\ref{def:transitivedelivery} to converge towards
optimal partitioning. Figure~\ref{fig:add} illustrates its behavior on
a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition. They initialize their own
state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition. At scale, such \emph{scoped flooding} saves bandwidth by
limiting generated traffic to subsets of
processes~\cite{wang2015prodiluvian}. In Figure~\ref{fig:addD},
processes discard last transiting messages. The system converged to
the optimal partitioning.  Transitive relationships ensure that each
process gets its closest source while accumulation of weights ensures
that messages propagation terminates.  Interestingly, while the
receipt order of messages does not impact on local control information
($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1}) \Leftrightarrow
r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
\TODO{d_b(\alpha_a^{1})}$), it impacts on control information
broadcast in the network ($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1})
\implies b_b(\alpha_{b}^{1.5}) \cdot b_b(\alpha_{b}^{1})$ while
$r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
b_b(\alpha_a^{1})$).

@@

One could solve this issue by using a conflict-free replicated data
type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
require eventual delivery of messages to ensure convergence. All
processes need to receive, deliver, hence broadcast all
operations. Some processes may receive operations unnecessary to their
correct functioning, for these operations did not happen in their
locality.  One could also solve this issue by removing partitions that
were not advertised for a defined
time~\cite{hemmati2015namebased}. However, relying on physical timeout
could lead to either premature removals of partitions when they are
still operating; or slow convergence where processes believe they
belong to a partition that was removed (\TODO{plot ?}). In addition,
since timeouts imply a continuous maintenance of partitions, such
partitioning protocol incurs an overhead even in quiet contexts
without dynamic partitions.

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{fig:del}Partition removals cannot rely only on
    current partition, for it may lead to either inconsistent
    partitioning, or every process receiving every broadcast.}
\end{figure*}

\begin{problem}[Consistent partitioning]
  How to enable \emph{consistent} dynamic optimal partitioning in
  dynamic network using scoped flooding?
\end{problem}
